### 2022-05-22 sections/conferences-full.tex
Update conferences-full.tex
LPPL v1.3c

\begin{benumerate}{66}

\item{\small González-Bustamante, B. (2022). {\itshape Resignation Calls and Dismissals of Ministers in Latin America}. Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, San Francisco, USA.}\vspace{1mm}

\item{\small González-Bustamante, B. (2022). {\itshape Resignation Calls and Ministerial Turnover in Latin America}. Presentation delivered at the Society for Latin American Studies Annual Conference, Bath, UK.}\vspace{1mm}

>>>>

\begin{benumerate}{68}

\item{\small González-Bustamante, B., \& Aguilar, D. (2022). {\itshape Territorial Patterns in Digital Development and Open Government: Evidence from Chilean Municipalities}. Presentation delivered at the XI Latin American Congress of Political Science, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2022). {\itshape Resignation Calls and Dismissals of Ministers in Latin America: ata Gathering using NLP and Machine Learning}. Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2022). {\itshape Insights of a Number of Ongoing Research on Elites in Latin America: Topics, Methods and Possibilities for Comparison}. Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, Virtual.}\vspace{1mm}

\item{\small González-Bustamante, B. (2022). {\itshape Resignation Calls and Ministerial Turnover in Latin America: Notes on Data Gathering using Machine Learning}. Presentation delivered at the Society for Latin American Studies Annual Conference, Bath, UK.}\vspace{1mm}
